---
title: "Statistical assignment 5, version 2"
author: "[add your name here] [add your candidate number here - mandatory]"
date: "[add date here]"
output: github_document
---

```{r setup, include=FALSE}
# Please note these options.
# This tells R Markdown that we want to show code in the output document.
knitr::opts_chunk$set(echo = TRUE)
# Switching off messages and warnings in the output document. 
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
# Switching on caching to make things faster (don't commit cache files on Github).
knitr::opts_chunk$set(cache = TRUE)
```

## Factors (10 points)

```{r}
colour <- c(rep("Green", 3), rep("Red", 7), rep("Yellow", 5))
```

Convert *colour* into a factor with the levels in the following order: "Yellow", "Red", "Green".

```{r}
...

```

## Vectorised functions (20 points)

You need to complete the file path here.

```{r}
library(tidyverse)
Stable <- read_tsv("...\xwavedat.tab")
```

Create a vector of lengths of variable names in the *Stable* data frame. (For example, "pidp" has length 4 as it has four characters). Calculate the average length of the variable name.

```{r}
...
```

## Functions (20 points)

In the Understanding Society data -9 often signifies missing values. For example:

```{r}
table(Stable$sex)
```

Write a function that takes a vector as an argument, converts -9 to NA and returns the recoded vector. Test it with the *sex* variable.

```{r}
codeNA <- function(x){
...
}
table(Stable$sex, useNA = "always")
table(codeNA(Stable$sex), useNA = "always")

```

## For() loops (20 points)

Write a for() loop to count the number of columns in Stable that contain at least one occurence of -9. Return this number.

```{r}
...

```

## map() functions (30 points)

Now perform the same operation as in the previous question using the map() family of functions.

```{r}
...

```
